\newcommand{\NibCompanyHeading}{%
  \EmployerHeader{nib Health Funds}{\NibLogo}%
}

\newcommand{\NibLeadHeading}{%
  \EmployerRole{Lead Data Scientist}{Machine learning}{September 2022--January 2024}%
}

\newcommand{\NibLeadRole}{%
  \NibLeadHeading
  \RoleContext{Senior member of a machine-learning team delivering work across operations and marketing, combining applied modelling with shared computing and research-to-production practices.}
  \CVBulletsStart
    \item Contributed to machine-learning projects across operations and marketing using survival analysis, time-series modelling, reinforcement-learning methods and language models.
    \item Helped build Soma Factory, an AWS-based machine-learning compute environment, and established reusable practices for moving research into production.
    \item Mentored junior data scientists through modelling, engineering and delivery work.
  \CVBulletsEnd
}

\newcommand{\NibLeadRolePlatform}{%
  \NibLeadHeading
  \RoleContext{Worked across modelling and team enablement, helping turn a collection of research activities into a more repeatable path for scientific computing and delivery.}
  \CVBulletsStart
    \item Helped build Soma Factory, an AWS-based machine-learning compute environment supporting shared scientific work.
    \item Established reusable workflows and templates for moving research into production, while contributing hands-on modelling across operational and marketing problems.
    \item Mentored junior data scientists in model development and production delivery.
  \CVBulletsEnd
}

\newcommand{\NibDigitalScientistRole}{%
  \EmployerRole{Digital Data Scientist}{Digital}{August 2019--August 2022}
  \RoleContext{Led behavioural data, experimentation, reporting and machine-learning delivery across nib's web and app assets.}
  \CVBulletsStart
    \item Grew the team from one person to three while establishing shared analytical and delivery practices.
    \item Structured semi-structured web and app behavioural data into accessible analytical tables using dbt.
    \item Connected real-time and batch machine-learning outputs with web systems using Tealium and Optimizely, bringing data engineering, experimentation and production ML into the same delivery loop.
    \item Supported commercial decisions through behavioural analysis and experimentation without separating model development from measurement.
  \CVBulletsEnd
}

\newcommand{\NibDigitalAnalystRole}{%
  \EmployerRole{Digital Analyst}{Digital}{November 2015--July 2019}
  \RoleContext{Worked with UX designers and developers to understand acquisition and retention behaviour and improve the website through controlled experimentation.}
  \CVBulletsStart
    \item Designed and evaluated website experiments, helping develop the A/B testing practices used by the optimisation team.
    \item Analysed acquisition and retention behaviour and developed automated reporting for teams across the organisation.
    \item Worked with UX designers, developers and the University of Newcastle Cognition Lab on experimentation and machine-learning research.
  \CVBulletsEnd
}

\newcommand{\StudentInformationRole}{%
  \EmployerHeader{University of Newcastle}{\UniversityLogo}%
  \EmployerRole{Student Information Assistant}{Marketing and engagement}{March 2012--March 2015}
  \CVBulletsStart
    \item Evaluated marketing campaigns and combined survey, engagement and social-media data in automated reporting for university services.
    \item Organised promotional staff while maintaining a direct connection with the student body.
  \CVBulletsEnd
}

\newcommand{\NibExperienceStandard}{%
  \NibCompanyHeading
  \NibLeadRole
  \RoleGap
  \NibDigitalScientistRole
  \RoleGap
  \NibDigitalAnalystRole
  \EmployerGap
  \StudentInformationRole
}

\newcommand{\NibExperiencePlatform}{%
  \NibCompanyHeading
  \NibLeadRolePlatform
  \RoleGap
  \NibDigitalScientistRole
  \RoleGap
  \NibDigitalAnalystRole
  \EmployerGap
  \StudentInformationRole
}
