\newcommand{\HunterRoleHeading}{%
  \EmployerHeader{\HunterLogo}{Hunter Water}%
  \EmployerRole{Lead Machine Learning Scientist}{Intelligent Networks}{August 2024--present}%
}

\newcommand{\HunterAppliedExperience}{%
  \HunterRoleHeading
  \CVBulletsStart
    \item Helped establish and expand secure Azure Machine Learning development and deployment practices, connecting Azure ML with Snowflake, Databricks, Azure Data Factory and enterprise data systems.
    \item Built reusable project and pipeline templates, shared Python utilities and Azure DevOps CI/CD patterns so research can move through a consistent, governed delivery path.
    \item Develops work across trunk-main failure prediction, pipe asset renewal, pump maintenance optimisation, demand forecasting, digital-meter reconstruction and water-quality risk using survival analysis, forecasting, anomaly detection, optimisation and explainability.
    \item Uses dbt for reproducible data preparation and publication, with MLflow experiment tracking and model registration supporting clearer development and production separation.
    \item Connects model outputs with GIS, SCADA, Snowflake, Databricks and Power BI according to each product's delivery stage, linking modelling with engineering, maintenance and operational workflows.
  \CVBulletsEnd
}

\newcommand{\HunterPlatformExperience}{%
  \HunterRoleHeading
  \CVBulletsStart
    \item Helped establish secure Azure ML development and deployment practices with clearer separation between research and production environments.
    \item Built reusable ML product and pipeline templates, shared Python utilities and environment patterns that reduce duplication across scientific work.
    \item Established Azure DevOps CI/CD patterns for training and scoring workflows, with MLflow experiment tracking and governed model registration.
    \item Developed dbt-based preparation and publication pipelines across Snowflake and enterprise data systems, supporting reproducible inputs and governed downstream products.
    \item Designs the environment for use by scientists, engineers, analysts and research collaborators rather than relying on a central team to run every model manually.
  \CVBulletsEnd
}

\newcommand{\HunterResearchExperience}{%
  \HunterRoleHeading
  \CVBulletsStart
    \item Develops applied ML for water infrastructure, including asset failure, demand, pump maintenance, digital-meter reconstruction and water-quality problems.
    \item Applies survival analysis, temporal modelling, anomaly detection, optimisation, uncertainty estimation and explainability to decisions in a regulated, safety-relevant setting.
    \item Helps carry research into governed Azure ML workflows using reusable pipelines, dbt, MLflow, Snowflake and Azure DevOps.
    \item Connects modelling with GIS, SCADA, Databricks and Power BI so outputs can enter engineering and operational workflows as products mature.
  \CVBulletsEnd
}

\newcommand{\HunterAppliedPortfolio}{%
  \Section{Applied ML portfolio}
  \CapabilityLine{Infrastructure risk}{Trunk-main failure prediction, broader pipe-renewal modelling and wastewater pump maintenance optimisation.}
  \CapabilityLine{Monitoring and demand}{Water-demand forecasting, digital-meter consumption reconstruction, and water-quality risk and anomaly modelling.}
  \CapabilityLine{Scientific methods}{Survival analysis, time-series modelling, gradient boosting, probabilistic reconstruction, optimisation, uncertainty estimation and explainability.}
  \CapabilityLine{Operational interfaces}{GIS, SCADA, Snowflake, Databricks and Power BI, with field-service and maintenance integration considered at product delivery stage.}
}

\newcommand{\HunterPlatformCapability}{%
  \Section{Platform capability}
  \CapabilityLine{Development}{Azure Machine Learning, reusable product templates, shared Python utilities, environment and dependency management.}
  \CapabilityLine{Delivery}{Azure DevOps, CI/CD, reproducible training and scoring pipelines, MLflow tracking and governed model registration.}
  \CapabilityLine{Data}{Snowflake, Databricks, Azure Data Factory, SQL and dbt-based preparation and publication pipelines.}
  \CapabilityLine{Operating model}{A self-service scientific environment designed for use across disciplines, with common technical standards and production separation.}
}

\newcommand{\HunterTechnicalLeadership}{%
  \Section{Platform and technical leadership}
  \CapabilityLine{Reusable delivery}{Common product templates, pipeline patterns and shared utilities give new scientific work a maintained starting point.}
  \CapabilityLine{Governed practice}{Development and production separation, tracked experiments, registered models and reproducible scoring make delivery reviewable.}
  \CapabilityLine{Cross-disciplinary use}{Technical standards are designed for scientists, engineers, analysts and research collaborators working in the same environment.}
  \CapabilityLine{Practice development}{Supports other practitioners through reusable examples, delivery guidance and technical review while retaining hands-on modelling responsibility.}
}

\newcommand{\ResearchEngineeringPractice}{%
  \Section{Research engineering practice}
  \CapabilityLine{Reproducible execution}{Research is carried through reusable Azure ML pipelines, tracked experiments, versioned code and governed data preparation.}
  \CapabilityLine{Domain collaboration}{Methods are developed with scientists, engineers, analysts and academic collaborators who understand the physical and operational constraints.}
  \CapabilityLine{Operational validation}{Evaluation considers uncertainty, interpretability and how outputs enter engineering or monitoring workflows, not benchmark performance alone.}
}
