\newcommand{\AppliedProfile}{%
  \CVHeader
    {Applied Machine-Learning Scientist}
    {Scientific modelling \textperiodcentered{} ML platforms \textperiodcentered{} operational decision systems}
    {Applied machine-learning scientist working across scientific modelling, ML platform engineering, operational deployment, research and technical leadership. Takes difficult infrastructure problems from statistically credible analysis to governed systems used by engineers, scientists, analysts and operators in regulated, safety-relevant settings. Builds the shared infrastructure and standards needed to keep those systems reproducible and maintainable.}%
}
\newcommand{\PlatformProfile}{%
  \CVHeader
    {ML Platform Lead \textperiodcentered{} Applied Scientist}
    {Governed delivery \textperiodcentered{} reusable ML systems \textperiodcentered{} scientific computing}
    {Machine-learning platform lead and applied scientist who connects research, data engineering and governed production delivery. Builds reusable environments, pipelines and standards that let scientists and engineers develop, register, score and publish models through a common path. Retains hands-on depth in infrastructure forecasting, risk modelling and operational integration.}%
}

\newcommand{\ResearchProfile}{%
  \CVHeader
    {Research Engineer \textperiodcentered{} Applied Machine Learning}
    {Scientific ML \textperiodcentered{} uncertainty \textperiodcentered{} production research systems}
    {Research engineer and applied machine-learning scientist working where scientific modelling meets production infrastructure. Develops statistically credible methods for sparse and changing observations, then carries them into governed systems that support engineering and operational decisions. Current computer-science research is grounded in live water-system problems.}%
}
