\newcommand{\PhDEntry}{%
  \Role{Doctor of Philosophy, Computer Science}{University of Newcastle}{Ongoing research}{Ongoing}
  {\fontsize{10}{12.8}\selectfont\RaggedRight
    \textbf{Working theme: Learning across sampling regimes in water monitoring.}
    Investigates how machine-learning systems can transfer from sparse, manually collected infrastructure observations to dense sensor streams while preserving uncertainty, interpretability, physical constraints and operational usefulness. The work is positioned as a computer-science contribution and grounded in live water-system problems, with parts developed through Hunter Water's production ML environment.\par}
  \vspace{4pt}
  \CVBulletsStart
    \item Studies domain adaptation under incompatible sampling regimes and constrained reconstruction of daily consumption from sparse manual readings using dense digital-meter observations for training and validation.
    \item Technical themes include probabilistic modelling, uncertainty calibration, temporal modelling, physics-informed constraints, sensor information gain and operational validation.
  \CVBulletsEnd
}

\newcommand{\PhDEntryCompact}{%
  \Role{Doctor of Philosophy, Computer Science}{University of Newcastle}{Ongoing research}{Ongoing}
  {\fontsize{10}{12.8}\selectfont\RaggedRight
    \textbf{Learning across sampling regimes in water monitoring.}
    Researches transfer from sparse manual infrastructure observations to dense sensor streams while preserving uncertainty, interpretability, physical constraints and operational value. The computer-science work is grounded in live water-system problems and parts are developed through Hunter Water's production ML environment.\par}
  \vspace{3pt}
  \CVBulletsStart
    \item Current studies address failure modes in time-series domain adaptation and constrained daily-consumption reconstruction from sparse meter readings.
  \CVBulletsEnd
}

\newcommand{\SelectedPublication}{%
  {\fontsize{9.9}{12.7}\selectfont\RaggedRight
    Warburton, T. M., Rush, L. D., Cullen, E. G. R., Wiener, J. H., McManus, B. T. K., Heath, L., \& Evans, D. (2023). The impact of homelessness, substance use, and mental illness on surgical inpatient outcomes in Australia. \textit{Asia Pacific Journal of Public Health, 35}(5), 335--341.
    \href{https://doi.org/10.1177/10105395231175563}{https://doi.org/10.1177/10105395231175563}\par}
}

\newcommand{\ResearchThemes}{%
  \CapabilityLine{Sampling-regime transfer}{Domain adaptation when source and target observations have incompatible temporal structure.}
  \CapabilityLine{Sparse-to-dense inference}{Constrained probabilistic reconstruction, uncertainty calibration and validation against digital-meter observations.}
  \CapabilityLine{Operational research}{Explainability, physical constraints, sensor information gain and evaluation in a live infrastructure setting.}
}
