\newcommand{\AppliedSkills}{%
  \CapabilityLine{Languages and data}{Python, R, SQL and dbt.}
  \CapabilityLine{Scientific ML}{Constrained conditional diffusion, transformer sequence models, survival analysis, forecasting, anomaly detection, optimisation, domain adaptation, uncertainty calibration and explainability.}
  \CapabilityLine{Platforms and delivery}{Azure Machine Learning, AWS SageMaker, Databricks, Snowflake, MLflow, Azure DevOps, CI/CD, Git, model registration and governed scoring.}
  \CapabilityLine{Operational systems}{GIS, SCADA, Power BI, web experimentation platforms and field-service or maintenance integration.}
}
\newcommand{\PlatformSkills}{%
  \CapabilityLine{Languages and data}{Python, R, SQL and dbt.}
  \CapabilityLine{Cloud and ML delivery}{Azure Machine Learning, AWS SageMaker, Databricks, Snowflake, MLflow, Azure DevOps, CI/CD, model registration and governed scoring.}
  \CapabilityLine{Software practice}{Shared Python libraries, Git, reusable project templates, reproducible pipelines, environment management and development/production separation.}
  \CapabilityLine{Applied methods}{Conditional diffusion, transformer sequence models, survival analysis, forecasting, anomaly detection, optimisation and uncertainty calibration.}
}

\newcommand{\ResearchSkills}{%
  \CapabilityLine{Languages and data}{Python, R, SQL, dbt and Git.}
  \CapabilityLine{Generative and scientific ML}{Constrained conditional diffusion, transformer sequence models, domain adaptation, survival analysis, temporal modelling, anomaly detection and optimisation.}
  \CapabilityLine{Research engineering}{Azure Machine Learning, AWS SageMaker, Databricks, Snowflake, MLflow, CI/CD, reproducible pipelines and governed scoring.}
  \CapabilityLine{Trust and operations}{Uncertainty calibration, probabilistic scoring, explainability, physical constraints, GIS, SCADA and Power BI integration.}
}
